\documentclass{manual}

\title{SkoleSYS Developer Documentation}

\makeindex			% tell \index to actually write the .idx file


\begin{document}

\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\begin{abstract}

\noindent
This document addresses the developer specific issues of SkoleSYS. It is
split up in two main parts - SkoleSYS library documentation and SkoleSYS
distribution tools (disttools).

SkoleSYS Library Documentation coveres the skolesys python package wich
is essentially all SkoleSYS logic e.g. client, server, configuration, SOAP
and more.

SkoleSYS Distribution Tools documents the three tools for deb-packaging,
APT distribution and install CD creation (skolesys-deb, skolesys-apt and 
skolesys-cd)

\end{abstract}

\tableofcontents

\chapter{SkoleSYS Distribution Tools (trunk/disttools)\label{disttools}}
The SkoleSYS Distribution Tools are just convenience tools I have made to make the job of distributing SkoleSYS fast and easy. That way I can keep the main focus on developing the SkoleSYS libraries and GUI. 

The \member{skolesys-apt} script can fetch content via subversion, tarballs or iso-files and place data where you want it redistributed on target filesystems. You can define symlinks and install-scripts (preinst, postinst, prerm, postrm) and setup file permissions. It is also possible to register a scripts to be run by \member{skolesys-apt} after content extraction (ie. pre-bytecompile python scripts). Once the debinfo files (control files for \member{skolesys-apt}) are in place building a file is as easy as executing one command - you can even setup automatic version ticking and group debian packages together by syncronizing their version number.

After building debian packages \member{skolesys-apt} is the tool for building an APT archive. You only need to setup one aptinfo file (control file for \member{skolesys-apt}) per distribution you target create a \member{distribution hieararchi}\footnote{A distribution hieararchi tells \member{skolesys-apt} which packages go into which distribution components and which computer architecture they are build for.}. \member{skolesys-apt} will automatically generate the \member{dists} and \member{pool} directory so they are ready to put on your distribution webserver.
\input{skolesys-deb}
\input{skolesys-apt}
%\input{skolesys-cd}


% \chapter{Debugging \label{debugging}}
%
% XXX Explain Py_DEBUG, Py_TRACE_REFS, Py_REF_DEBUG.

\chapter{SkoleSYS Package (trunk/system)\label{skolesys-pack}}
\input{skolesys-deb}
\input{skolesys-apt}


\input{devel.ind}			% Index -- must be last

\end{document}


